\begin{flushleft} \mbox{\textmd{ \normalsize SLAC-PUB-15999 }} \end{flushleft} { The Heavy Photon Search Test Detector }

### 2014-06-23 hps-testrun-nim.tex
Added funding agencies to ack.
Added slac pub to title

%\usepackage{url}
\usepackage{hyperref}

@@

% HPS stuff
\usepackage{color}
%\usepackage{multicol}
\newcommand{\Aprime}{A\ensuremath{^\prime}}
\newcommand{\ee}{e$^+$e$^-$}
\newcommand{\fluenceunit}{1~MeV~neutron~equivalent/cm\ensuremath{^2}}
\newcommand{\geant}{{\sc Geant4}}
\newcommand{\egs}{{\sc EGS5}}
\newcommand{\moliere}{Moli\`{e}re}
%\include{affiliations}

@@

@@

\title{The Heavy Photon Search Test Detector}

@@

This work has been supported by the US Department of Energy. Rouven Essig is supported in part by the 
Department of Energy Early Career research program DESC0008061 and by a Sloan Foundation 
Research Fellowship.

>>>>

@@

% HPS stuff
%\usepackage{url}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{color}
%\usepackage{multicol}
\newcommand{\Aprime}{A\ensuremath{^\prime}}
\newcommand{\ee}{e$^+$e$^-$}
\newcommand{\fluenceunit}{1~MeV~neutron~equivalent/cm\ensuremath{^2}}
\newcommand{\geant}{{\sc Geant4}}
\newcommand{\egs}{{\sc EGS5}}
\newcommand{\moliere}{Moli\`{e}re}
%\include{affiliations}
\fancypagestyle{firststyle}
{
  \fancyhf{}  % clear all header and footer fields
  \fancyhead[R]{SLAC-PUB-xxxx}  % puts the text on the top Right side
}
%\pagestyle{firststyle}
%\pagestyle{fancy}

\makeatletter
\let\ps@plain\ps@fancy 
\makeatother

@@

\thispagestyle{firststyle}

@@

%\title{The Heavy Photon Search Test Detector}
\title{
\begin{flushleft}
%       \mbox{\textmd{ \normalsize -PUB-13/020 }}
        \mbox{\textmd{ \normalsize SLAC-PUB-15999 }}
       \end{flushleft}
{
The Heavy Photon Search Test Detector
}
}

@@

This work has been supported by the US Department of Energy, French Centre National de la Recherche 
Scientifique and Italian Istituto Nazionale di Fisica Nucleare. Rouven Essig is supported in part by the 
Department of Energy Early Career research program DESC0008061 and by a Sloan Foundation 
Research Fellowship.
